\section*{Problem 1 - Attitude Control of Satellite}

\subsection*{Problem 1 a)} 

\textbf{What is the ground speed of the aircraft (numerical value) in the absence of wind?} \\
In the absence of wind, $V_w = 0$, we have $V_g = V_a = 580 km/h$.

\subsection*{Problem 1 b)}

\textbf{Write down two expressions for the sideslip (crab) angle $\beta$ in the absence of wind. One expression should depend on aircraft velocity and the other on aircraft heading.} \\

\begin{align}
    \beta &= \sin^{-1}\left( \frac{v_r}{\sqrt{u_r^2 + v_r^2+w_r^2}}\right ) \\
    \beta &= \chi_c - \psi
\end{align}

\subsection*{Problem 1 c)}

\textbf{Compute the Dutch-roll natural frequency and relative damping ratio for the aircraft. Can you,
very briefly with your own words, describe how the Dutch roll mode affect the yaw and roll
motion? How would the motion change with increased relative damping ratio?}

\begin{align}
    \lambda_{dutch-roll} = \frac{Y_v+N_r}{2 }\pm \sqrt{\left(\frac{Y_v+N_r}{2}\right)^2 - \left(Y_vN_r - N_vY_r\right)}
\end{align}

With the constants found from the state space model 

\begin{align}
    Y_V = -0.322 \\ 
    N_R = -0.32 \\
    N_V = 0.0426 \\
    Y_R = -180.44
\end{align}
We get 

\begin{align}
    \lambda = -0.321 \pm 2.77i \\
    \omega_n = 2.79 \\
    \zeta = 0.1147
\end{align}

Dutch roll will affect roll and yaw by inducing an oscillation in yaw which is "transferred" to roll. If you increase the damping ratio the oscillation will dampen faster. 


\subsection*{Problem 1 d)}

\textbf{Compute the spiral-divergence mode. Is the mode unstable?} \\
For the spiral-divergence mode we assume that $\dot{\bar{p}} = \Bar{p} = 0$ and that the rudder command is negligible. We have
\begin{align}
    \lambda_{spiral} &= \frac{N_rL_v - N_vL_r}{L_v} 
\end{align}

With the constants

\begin{align}
    L_v = -0.0657 \\
    L_r = 0.46
\end{align}

We get \\
\begin{align}
    \lambda_{spiral} = -0.022
\end{align}

Since $\lambda$ is less than 0 we do not have an unstable mode. 

\subsection*{Problem 1 e)}
\textbf{Compute the roll mode. Is the roll mode faster or slower than the spiral-divergence mode?} \\
We can find the roll mode by ignoring the heading dynamics and assuming a constant pitch angle. An approximation of the eigenvalue for the rolling mode is given by  
\begin{align}
    \lambda_{roll} &= L_p \\
    &= -2.87
\end{align}
This mode is faster, as the pole is more negative.


% Note that \mathbf can be used for bold letters in math mode (within equations and dollar signs). \boldsymbol can be used to get bold greek letters.  